PAPER TEMPLATE FOR ISMIR 2014

### 2014-04-27 paper/paper.tex
temporary commit for pulling

@@

\subsection{Melody Extraction}
\subsubsection{Task definition}
Melody extraction algorithms aim to produce a sequence of frequency values
corresponding to the pitch of the dominant melody from a musical recording
\cite{salamon:MelodyReview:IEEESPM13}. The estimated pitch is represented as a
time series of fundamental frequency ($f_0$) values in Hz sampled on a fixed
time grid (e.g.~every 10 ms). To evaluate the estimated sequence, a reference
sequence is generated by running a pitch tracker on the monophonic melody track
(requiring access to the multi-track recording session) and manually correcting
any mistakes made by the pitch tracker. The estimate is then evaluated against
the reference by comparing the two frequency sequences on a frame-by-frame
basis, and computing five global measures, first used in the MIREX 2005 AME
evaluation \cite{polinerMelodyEval}. The goal of these measures, defined below,
is to assess the algorithm's performance on two subtasks of melody extraction:
(1) pitch estimation, i.e.~how well the algorithm estimates the pitch of the
melody, and (2) voicing detection, i.e.~how well the algorithm determines when
the melody is present in a frame (a \textit{voiced} frame) or absent (an
\textit{unvoiced} frame). To allow evaluation of these two subtasks
independently, a melody extraction algorithm can provide a frequency estimate
even for frames it has determined to be unvoiced.

\subsubsection{Evaluation measures}
The following definitions are taken from
\cite{salamon:MelodyReview:IEEESPM13} with permission from the authors. Let the estimated melody pitch frequency
vector be $\mathbf{f}$, and the true sequence (reference) be $\mathbf{f}^*$. Let
us also define a voicing indicator vector $\mathbf{v}$, whose $\tau^\text{th}$
element $v_\tau = 1$ when a melody pitch is detected, with corresponding ground
truth $\mathbf{v}^*$.  We also define an ``unvoicing'' indicator $\bar{v}_\tau =
1 - v_\tau$.  Recall that an algorithm may report an estimated melody pitch
($f_\tau > 0$) even for times where it reports no voicing ($v_\tau = 0$).   
Then the measures are:
\begin{itemize}
  \item \textbf{Voicing Recall Rate}: The proportion of frames labeled as
  melody frames in the reference that are estimated as melody frames by the
  algorithm.
\begin{equation}
\text{Rec}_\text{vx} = \frac{\sum_\tau v_\tau v^*_\tau}{\sum_\tau v^*_\tau}
\end{equation}

  \item \textbf{Voicing False Alarm Rate}: The proportion of frames
  labeled as non-melody in the reference that are mistakenly estimated as
  melody frames by the algorithm.
\begin{equation}
\text{FA}_\text{vx} = \frac{\sum_\tau v_\tau \bar{v}^*_\tau}{\sum_\tau \bar{v}^*_\tau}
\end{equation}

  \item \textbf{Raw Pitch Accuracy}: The proportion of melody frames in the
  reference for which $f_\tau$ is considered
  correct (i.e.~within half a semitone of the ground
  truth $f^*_\tau$).
\begin{equation}
\text{Acc}_\text{pitch}= \frac{\sum_\tau v^*_\tau \mathcal{T}\left[\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau) \right] }{\sum_\tau v^*_\tau}
\end{equation}
where $\mathcal{T}$ is a threshold function defined by:
\begin{equation}
\mathcal{T}[a] = \begin{cases}
1 \quad \text{if } |a| < 0.5 \\
0 \quad \text{if } |a| \ge 0.5
\end{cases}
\end{equation}
and $\mathcal{M}$ maps a frequency in Hertz to a melodic 
axis as a real-valued number of semitones above an arbitrary
reference frequency $f_\text{ref}$:
\begin{equation}
\mathcal{M}(f) = 12 \log_2\left( \frac{f}{f_\text{ref}} \right)
\end{equation}

  \item \textbf{Raw Chroma Accuracy}: As raw pitch accuracy, except
  that both the estimated and reference $f_0$ sequences are mapped onto a
  single octave. This gives a measure of pitch accuracy which ignores octave
  errors, a common error made by melody extraction systems:
\begin{equation}
\text{Acc}_\text{chroma}= \frac{\sum_\tau v^*_\tau \mathcal{T}\left[\left<\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau)\right>_{12} \right] }{\sum_\tau v^*_\tau}
\end{equation}
Octave equivalence is achieved by taking the difference between the semitone-scale pitch 
values modulo 12 (one octave), where
\begin{equation}
\left<a\right>_{12} = a - 12 \lfloor \frac{a}{12} + 0.5 \rfloor .
\end{equation}

  \item \textbf{Overall Accuracy}: this measure combines the performance of the
  pitch estimation and voicing detection tasks to give an overall performance
  score for the system. It is defined as the proportion of all frames
   correctly estimated by the algorithm, where for non-melody
  frames this means the algorithm labeled them as non-melody, and for melody
  frames the algorithm both labeled them as melody frames and provided a correct
  $f_0$ estimate for the melody (i.e.~within half a semitone of the
  reference):

\begin{equation}
\text{Acc}_\text{ov} 
= \frac{1}{L} \sum_\tau v^*_\tau \mathcal{T}\left[\mathcal{M}(f_\tau)-\mathcal{M}(f^*_\tau) \right] + \bar{v}^*_\tau \bar{v}_\tau 
\end{equation}
where $L$ is the total number of frames.
\end{itemize}

The performance of an algorithm on an entire music collection for a given
measure is obtained by averaging the per-excerpt scores for that measure over
all excerpts in the collection.

\subsubsection{Discussion}

% \subsection{Figures, Tables and Captions}
% 
% All artwork must be centered, neat, clean, and legible.
% All lines should be very dark for purposes of reproduction and art work should not be hand-drawn.
% The proceedings are not in color, and therefore all figures must make sense in black-and-white form.
% Figure and table numbers and captions always appear below the figure.
% Leave 1 line space between the figure or table and the caption.
% Each figure or table is numbered consecutively. Captions should be Times 10pt.
% Place tables/figures in text as close to the reference as possible.
% References to tables and figures should be capitalized, for example:
% see \figref{fig:example} and \tabref{tab:example}.
% Figures and tables may extend across both columns to a maximum width of 17.2cm.

% \begin{table}
%  \begin{center}
%  \begin{tabular}{|l|l|}
%   \hline
%   String value & Numeric value \\
%   \hline
%   Hello ISMIR  & 2014 \\
%   \hline
%  \end{tabular}
% \end{center}
%  \caption{Table captions should be placed below the table.}
%  \label{tab:example}
% \end{table}

@@

% \begin{thebibliography}{citations}
% 
% \bibitem {Author:00}
% E. Author:
% ``The Title of the Conference Paper,''
% {\it Proceedings of the International Symposium
% on Music Information Retrieval}, pp.~000--111, 2000.
% 
% \bibitem{Someone:10}
% A. Someone, B. Someone, and C. Someone:
% ``The Title of the Journal Paper,''
% {\it Journal of New Music Research},
% Vol.~A, No.~B, pp.~111--222, 2010.
% 
% \bibitem{Someone:04} X. Someone and Y. Someone: {\it Title of the Book},
%     Editorial Acme, Porto, 2012.
% 
% \end{thebibliography}

\bibliography{mir_eval}

>>>>

\def\eg{\emph{e.g.\/}}
\def\ie{\emph{i.e.\/}}
\def\etc{\emph{etc.\/}}
\def\etal{\emph{et al.\/}}

@@

\subsection{Segmentation}

Music segmentation evaluation metrics can be grouped into two main categories: boundary annotation, and structural annotation.
In the former, the task is to accurately predict the times of boundaries between adjacent segments (\eg, where a \emph{verse} transitions to a \emph{chorus}).
Structural annotation metrics are primarily concerned with the labeling task: correctly identifying multiple segments as belonging to the same or different classes.

In both tasks, we assume that annotations take the form of a partitioning of the track 
into intervals ${(s_i, t_i)}_{i=1}^m$, where $s_0=0$ denotes the beginning of track, 
$t_m$ denotes the end of the track, and $t_i = s_{i+1}$.
Structural annotation additionally requires that each interval be assigned a string
descriptor.

\subsubsection{Boundary annotation}

Within boundary annotation, there are two categories of evaluation metrics: detection,
and deviation~\cite{turnbull2007}.

Let $B_R$ ($B_E$) denote the set of unique interval boundary times in the reference 
(estimated) annotation, and let $W$ denote a tolerance window, typically either $0.5$s
or $3.0$s.

\subsubsection{Structural annotation}

\section{Footnotes and Figures}

\subsection{Footnotes}

Indicate footnotes with a number in the text.\footnote{This is a footnote.}
Use 8pt type for footnotes. Place the footnotes at the bottom of the page on which they appear.
Precede the footnote with a 0.5pt horizontal rule.

\subsection{Figures, Tables and Captions}

All artwork must be centered, neat, clean, and legible.
All lines should be very dark for purposes of reproduction and art work should not be hand-drawn.
The proceedings are not in color, and therefore all figures must make sense in black-and-white form.
Figure and table numbers and captions always appear below the figure.
Leave 1 line space between the figure or table and the caption.
Each figure or table is numbered consecutively. Captions should be Times 10pt.
Place tables/figures in text as close to the reference as possible.
References to tables and figures should be capitalized, for example:
see \figref{fig:example} and \tabref{tab:example}.
Figures and tables may extend across both columns to a maximum width of 17.2cm.

\begin{table}
 \begin{center}
 \begin{tabular}{|l|l|}
  \hline
  String value & Numeric value \\
  \hline
  Hello ISMIR  & 2014 \\
  \hline
 \end{tabular}
\end{center}
 \caption{Table captions should be placed below the table.}
 \label{tab:example}
\end{table}

@@

\section{Equations}

Equations should be placed on separated lines and numbered.
The number should be on the right side, in parentheses.

\begin{equation}
E=mc^{2}
\end{equation}

\section{Citations}

All bibliographical references should be listed at the end,
inside a section named ``REFERENCES,'' numbered and in alphabetical order.
Also, all references listed should be cited in the text.
When referring to a document, type the numbering square brackets
\cite{Author:00} or \cite{Author:00,Someone:10,Someone:04}.

\begin{thebibliography}{citations}

\bibitem {Author:00}
E. Author:
``The Title of the Conference Paper,''
{\it Proceedings of the International Symposium
on Music Information Retrieval}, pp.~000--111, 2000.

\bibitem{Someone:10}
A. Someone, B. Someone, and C. Someone:
``The Title of the Journal Paper,''
{\it Journal of New Music Research},
Vol.~A, No.~B, pp.~111--222, 2010.

\bibitem{Someone:04} X. Someone and Y. Someone: {\it Title of the Book},
    Editorial Acme, Porto, 2012.

\end{thebibliography}

%\bibliography{ismir2014template}
